Blum axioms and nondeterministic computation of functions

### 2016-05-17 paper.tex
paper.tex: Correct the function in the criticism of Hopcroft and Ullman's definition
I'm surprised no reviewer catched this "bug" in the paper. (To be fair,
one of them complained about the "formatting" of this proposition
--- this is what made me pay attention to it.)
paper.tex: Fix typo.

One important feature about the standard encodings of deterministic Turing machines
is the Universal Turing Machine Theorem:
the existence of a partial recursive function
$U: \{0, 1\}^* \times \{0, 1\}^* \to \{0, 1\}^*$
% Não sei se $U$ é um bom nome...
such that, if $w$ encodes the machine $M$,
then $U(m, x)$ is the result of running the machine $M$ on $x$.
A machines that compute $U$ is called \emph{universal Turing machine}.

@@

\vspace{6pt}
\begin{proposition}
    Define the partial function $f: \Sigma^* \times \Sigma^* \to \{0, 1\}$ by
    \begin{equation*}
        f(w, x) = \begin{cases}
            1, & \text{if the machine $w$ does not halt on $x$.} \\
            \text{undefined}, &\text{if $w$ never halts on $x$.}
        \end{cases}
    \end{equation*}
    This function can be computed by a nondeterministic Turing machine under
    Hopcroft and Ullman's definition.
\end{proposition}
\vspace{-3pt}

@@

Thus, we only enumerate computable functions.
to show the universal machine theorem and the $S_{mn}$,
we can simply first convert the machine in question to a deterministic machine
and use their theorems;
thus, this definition yields an acceptable Gödel numbering.
And, by counting the number of steps of the deepest branch,
we have a Blum complexity measure.

>>>>

One important feature about the standard encodings of deterministic Turing machines
is the Universal Turing Machine Theorem:
the existence of a partial recursive function
$U: \{0, 1\}^* \times \{0, 1\}^* \to \{0, 1\}^*$
such that, if $w$ encodes the machine $M$,
then $U(m, x)$ is the result of running the machine $M$ on $x$.
A machines that compute $U$ is called \emph{universal Turing machine}.

@@

\vspace{6pt}
\begin{proposition}
    Define the partial function $f: \Sigma^* \times \Sigma^* \to \{0, 1\}$ by
    \begin{equation*}
        f(w, x) = \begin{cases}
            1, & \text{if the machine $w$ does not halt on $x$.} \\
            \text{undefined}, &\text{if $w$ halts on $x$.}
        \end{cases}
    \end{equation*}
    This function can be computed by a nondeterministic Turing machine under
    Hopcroft and Ullman's definition.
\end{proposition}
\vspace{-3pt}

@@

Thus, we only enumerate computable functions.
To show the universal machine theorem and the $S_{mn}$,
we can simply first convert the machine in question to a deterministic machine
and use their theorems;
thus, this definition yields an acceptable Gödel numbering.
And, by counting the number of steps of the deepest branch,
we have a Blum complexity measure.
